Representable cylindric algebras of dimension $\omega$: the aspects of canonicity and axiomatisability

### 2021-07-10 filtration-stuff/NewText.tex
cylindric background

@@

\begin{defin}
  Let $\langle \mathcal{M}_1, x \rangle$ and $\langle \mathcal{M}_2, y \rangle$ be models with designated points and $r < \omega$. The $r$-round bisimulation game $\mathcal{G}(\mathcal{M}_1, \mathcal{M}_2, x, y)$ is played by two players, $\forall$ (Abelard, man) and $\exists$ (Heloise, woman). The rules of the game are the following:
  \begin{enumerate}
    \item ({\bf Round 0}) $\exists$ wins, if $x \equiv_0 y$. Otherwise, $\forall$ wins.
    \item ({\bf Round $n+1$}) Let $n + 1 < r$. Suppose rounds $0, \dots, n$ have been played.
    The $n$-th position is a pair $(x_n, y_n)$.
    $\forall$ chooses $x_{n + 1}$ (or $y_n \in W_2$) with $x_n R_1 x_{n + 1}$ (or $y_n R_1 y_{n + 1}$). $\exists$ chooses $y_{n + 1}$ ($x_{n + 1}$) with $y_n R_1 y_{n + 1}$ (or $y_n R_1 y_{n + 1}$) and $x_{n + 1} \equiv_0 y_{n + 1}$.
    $\forall$ ($\exists$) wins, if $\exists$ ($\forall$) cannot move.
  \end{enumerate}
  $\exists$ wins the game after $r$ rounds. $\forall$ wins the game, if there exists $k < r$ such that $\forall$ wins in {\bf Round $k$}.
\end{defin}

There are two $n$-equivalences for formulas and games (the first one is due to Fine \cite{fine1974logics}). These definitions are equivalent, this is due to Stirling.

@@

  \begin{itemize}
  \item $(\mathcal{M}_1, x) \equiv_n (\mathcal{M}_2, y)$ iff for every $\varphi$ such that
  $md(\varphi) \leq n$ we have $\mathcal{M}_1, x \models \varphi$ iff $\mathcal{M}_2, y \models \varphi$.
  \item $(\mathcal{M}_1, x) \equiv_n (\mathcal{M}_2, y)$ iff $\exists$ has a winning strategy in $\mathcal{G}(\mathcal{M}_1, \mathcal{M}_2, x, y)$.
  \end{itemize}
\end{defin}

@@

The ${\bf K5}$-closure (the Euclidean Horn closure of a binary relation) has the following equivalent definitions:
\begin{lemma} \label{equivHorn}
  Let $\mathcal{F} = \langle W, R \rangle$ be a Kripke frame and $R \subseteq R^{\bf K5}$.
  The following conditions are equivalent:

@@

\begin{enumerate}
  \item $(1) \Rightarrow (2)$
  Let us show that if $R^{E}$ is the smallest Euclidean relation containing $R$, then $R^{E} = \bigcup \limits_{i < \omega} R_i$. There are two inclusions:
  \begin{itemize}
    \item $R^{E} \subseteq \bigcup \limits_{i < \omega} R_i$. Recall that $R^{E}$ has the form (?):
    \begin{center}
      $R^{E} = \bigcap \{ R' \: | \: R \subseteq R', \forall a, b \in W \: R'(a,b) \Rightarrow \exists x \in W \: R'(x, a) \: \& \: R'(x, b)\}$
    \end{center}

    \item $\bigcup \limits_{i < \omega} R_i \subseteq R^{E}$.
    Let us show that $x R_n y$ for each $n < \omega$ implies $x R^E y$ by induction on $n$.
    If $n = 0$, then $x R y$, thus, $x R^{E} y$, since $R$ is a subrelation of $R^{E}$.
    Suppose $n = m + 1$ and $x R_{m + 1} y$. Let us show that $x R^{E} y$.
    From $x R_{m + 1} y$, one has $(x, y) \in R^n \cup (R^{-1}_n \circ R_n)$. There are two cases:
    \begin{itemize}
      \item $x R^n y$, one needs to merely apply the IH.
      \item $x R^{-1}_n \circ R_n y$. Then $\exists z \in W \: x R^{-1}_n z \: \& \: z R_n$. That is,
      $z R_n x$ and $z R_n y$ for some $z$. $R_n$ is already a subrelation of $R^E$. Thus,
      $z R^{E} x$ and $z R^{E} y$. That implies $x R^{E} y$.
    \end{itemize}
  \end{itemize}
  \item $(2) \Rightarrow (3)$
  Let $(x, y) \in R_m$, let us the statement by induction on $m$.
  \begin{enumerate}
    \item Suppose $m = 0$, then $x R y$, and the statement is shown putting $n = 0$.
    \item Suppose $m = p + 1$ and $x R_{p + 1} y$.
    Assume that either $x R y$ or $\exists z_1, \dots, z_p$ with $z_1 R x$ and $z_{p - 1} R y$ and for each $1 < i \leq p$ one has
    either $z_{i - 1} R z_i$ or $z_i R z_{i - 1}$.

    $x R_{p + 1} y$ implies $(x, y) \in R_{p} \cup (R^{-1}_p \circ R_p)$. If $(x, y) \in R_{p}$, then we merely apply the IH.
    Suppose $(x, y) \in R^{-1}_p \circ R_p$, then $(z, x) \in R_p$ and $(z, y) \in R_p$
  \end{enumerate}
  \item $(3) \Rightarrow (4)$
  Suppose either $x R y$ or there exist $n \geq 1$ and $z_1, \dots, z_n$ with $z_1 R x$ and $z_{n - 1} R y$ and for each $1 < i \leq n$ one has either $z_{i - 1} R z_i$ or $z_i R z_{i - 1}$.
  If $x R y$, then we are done. Otherwise there exists $n \geq 1$ with the condition above. Then $(x, y) \in R_{n + 1}$ that follows from the condition.
  \item $(4) \Rightarrow (1)$
\end{enumerate}
\end{proof}

@@

A binary relation $R \subseteq W \times W$ is called $i,j$-Euclidean for $i, j < \omega$, if for each $x, y, z$ such that $x R^{i} y$ and $x R^{j} z$ implies $x R z$.

@@

Let $R$ be a binary relation on $W \neq \emptyset$, then the $i,j$-Euclidean closure of $R$ (where $i, j < \omega$), denoted as $R^{{\bf K}5_{i,j}}$, is a binary relation defined recursively as follows:
\begin{enumerate}
  \item $R_0 = R$
  \item $R_{n + 1} = R_n \cup (((R_n)^{-1})^i \circ {R_n}^j)$
  \item $R^{E_{i,j}} = \bigcup \limits_{k < \omega} R_k$
\end{enumerate}

@@

\begin{theorem}
$md({\bf K5}^{i,j}) = 1 + j + i$, if $i \neq 0$.
\end{theorem}

@@

@@

\begin{proof}
  Let $\mathcal{M} = \langle W, R, \vartheta \rangle$ and $\Gamma$ a finite $\operatorname{Sub}$-closed of formulas. We extend $\Gamma$ as
  \begin{center}
    $\Delta = \Gamma \cup \operatorname{Sub}\{  \Diamond^{i} \psi \: | \: \Box \psi \in \Gamma \} \cup \operatorname{Sub}\{ \Box^{j} \Diamond \psi \: | \: \Diamond \psi \in \Gamma \}$
  \end{center}
  Let $(\hat{x}, \hat{y}) \in R^{E_{i,j}}$, $\mathcal{M}, x \models \Box \psi$ for $\Box \psi$ in $\Delta$.
  If $n = 0$, then the statement is obvious. Suppose $n = 1$.
  Then $(\hat{x}, \hat{y}) \in R_{min} \cup (((R_{min})^{-1})^i \circ {R_{min}}^j)$. Consider the second alternative. Then there exists $\hat{z}$ such that $(\hat{x}, \hat{z}) \in ((R_{min})^{-1})^i $ and $(\hat{z}, \hat{y}) \in {R_{min}}^j$.

@@

\begin{proof}
  Let $\mathcal{M} = \langle W, R_1, R_2, \vartheta \rangle$ be an $\mathcal{L}_1 * \mathcal{L}_2$.
  We define a notation $\nabla = \{ \neg \Diamond, \Diamond \neg, \Diamond \}$.

>>>>

\theoremstyle{exercise}
\newtheorem{exercise}{Exercise}

@@

\begin{defin}
  Let $\langle \mathcal{M}_1, x \rangle$ and $\langle \mathcal{M}_2, y \rangle$ be models with designated points and $r < \omega$. The $r$-round bisimulation game $\mathcal{G}_r(\mathcal{M}_1, \mathcal{M}_2, x, y)$ is played by two players, $\forall$ (Abelard, man) and $\exists$ (Heloise, woman). The rules of the game are the following:
  \begin{enumerate}
    \item ({\bf Round 0}) $\exists$ wins, if $x \equiv_0 y$. Otherwise, $\forall$ wins.
    \item ({\bf Round $n+1$}) Let $n + 1 < r$. Suppose rounds $0, \dots, n$ have been played.
    The $n$-th position is a pair $(x_n, y_n)$.
    $\forall$ chooses $x_{n + 1}$ (or $y_n \in W_2$) with $x_n R_1 x_{n + 1}$ (or $y_n R_1 y_{n + 1}$). $\exists$ chooses $y_{n + 1}$ ($x_{n + 1}$) with $y_n R_1 y_{n + 1}$ (or $y_n R_1 y_{n + 1}$) and $x_{n + 1} \equiv_0 y_{n + 1}$.
    $\forall$ ($\exists$) wins, if $\exists$ ($\forall$) cannot move.
  \end{enumerate}
  $\exists$ wins the game after $r$ rounds. $\forall$ wins the game, if there exists $k < r$ such that $\forall$ wins in {\bf Round $k$}.
\end{defin}

There are two $n$-equivalences for formulas and games (the first one is due to Fine \cite{fine1974logics}).

@@

  \begin{itemize}
  \item $(\mathcal{M}_1, x) \equiv_n (\mathcal{M}_2, y)$ iff for every $\varphi$ such that
  $md(\varphi) \leq n$ we have $\mathcal{M}_1, x \models \varphi$ iff $\mathcal{M}_2, y \models \varphi$.
  \item $(\mathcal{M}_1, x) \equiv_n (\mathcal{M}_2, y)$ iff $\exists$ has a winning strategy in $\mathcal{G}_n(\mathcal{M}_1, \mathcal{M}_2, x, y)$.
  \end{itemize}
\end{defin}

\begin{lemma} [See \cite{goranko20075}] \label{bisimequiv}

  The definitions of $n$-equivalence are equivalent for weak Kripke models.
\end{lemma}

@@

The ${\bf K5}$-closure (the Euclidean Horn closure of a binary relation) has the following equivalent definitions:
\begin{lemma} \label{equivHorn}
  Let $\mathcal{F} = \langle W, R \rangle$ be a Kripke frame. The following are equivalent:

@@

@@

\begin{defin}
A binary relation $R \subseteq W \times W$ is called $i,j$-Euclidean for $i, j < \omega$, if for each $x, y, z$ such that $x R^{i} y$ and $x R^{j} z$ implies $x R z$.
\end{defin}

@@

Let $R$ be a binary relation on $W \neq \emptyset$, then the $i,j$-Euclidean closure of $R$ (where $i, j < \omega$), denoted as $R^{{\bf K}5_{i,j}}$, is a binary relation defined recursively as follows:
\begin{enumerate}
  \item $R_0 = R$
  \item $R_{n + 1} = R_n \cup (((R_n)^{-1})^i \circ {R_n}^j)$
  \item $R^{{\bf K}5_{i,j}} = \bigcup \limits_{k < \omega} R_k$
\end{enumerate}

@@

\begin{exercise}
$md({\bf K5}) = 2$.
\end{exercise}

\begin{proof}
  For the upper bound, let us show that $\equiv_2 = \equiv_3$ in every weak canonical model of ${\bf K5}$, namely $\mathcal{L}_{\bf K5} \upharpoonright k$ for $k < \omega$.
  For that, we show that if $\exists$ can win $\mathcal{G}_2(\mathcal{L}_{\bf K5} \upharpoonright k, \Gamma, \Delta)$ (where $\Gamma$ and $\Delta$ are maximal consistent ${\bf K5} \upharpoonright k$-theories), then she can the game $\mathcal{G}_2(\mathcal{L}_{\bf K5} \upharpoonright k, \Gamma, \Delta)$ as well.

  If $\exists$ has a winning strategy in $\mathcal{G}_2(\mathcal{L}_{\bf K5} \upharpoonright k, \Gamma_0, \Delta_0)$, then, by Lemma~\ref{bisimequiv}, $\langle \mathcal{L}_{\bf K5} \upharpoonright k, \Gamma_0 \rangle \equiv_2 \langle \mathcal{L}_{\bf K5} \upharpoonright k, \Delta_0 \rangle$.

  Therefore, $\Gamma_0$ and $\Delta_0$ consist of the same formulas whose modal depth is less than or equal to $2$.

  Suppose $(\Gamma_2, \Delta_2)$ is the second position. Clearly $\Gamma_2 \equiv_0 \Delta_2$

  Let us assume that $\forall$ picks $\Gamma_3$ such that $\Gamma_2 R_{{\bf K5} \upharpoonright k} \Gamma_3$. $\exists$ has to find a proper response, namely $\Delta_3$, to win the game.

\begin{exercise}
  Let $i = j$, then $md({\bf K5}^{i,i}) = i + 1$. So ${\bf K5}^{i,i}$ is locally finite.
\end{exercise}

@@

\begin{theorem}
$md({\bf K5}^{i,j}) = 1 + j + i$, where $i > 0$.
\end{theorem}

@@

\begin{proof}
  Let $\mathcal{M} = \langle W, R, \vartheta \rangle$ and $\Gamma$ a finite $\operatorname{Sub}$-closed of formulas. We extend $\Gamma$ as
  \begin{center}
    $\Delta = \Gamma \cup \operatorname{Sub}\{  \Diamond^{i} \psi \: | \: \Box \psi \in \Gamma \} \cup \operatorname{Sub}\{ \Box^{j} \Diamond \psi \: | \: \Diamond \psi \in \Gamma \}$
  \end{center}
  Let $(\hat{x}, \hat{y}) \in R^{{\bf K}5_{i,j}}$, $\mathcal{M}, x \models \Box \psi$ for $\Box \psi$ in $\Delta$.
  If $n = 0$, then the statement is obvious. Suppose $n = 1$.
  Then $(\hat{x}, \hat{y}) \in R_{min} \cup (((R_{min})^{-1})^i \circ {R_{min}}^j)$. Consider the second alternative. Then there exists $\hat{z}$ such that $(\hat{x}, \hat{z}) \in ((R_{min})^{-1})^i $ and $(\hat{z}, \hat{y}) \in {R_{min}}^j$.

@@

\begin{proof}
  Let $\mathcal{M} = \langle W, R_1, R_2, \vartheta \rangle$ be an $\mathcal{L}_1 * \mathcal{L}_2$-model. We define a notation $\nabla = \{ \neg \Diamond, \Diamond \neg, \Diamond \}$.

### 2021-07-10 problem-5/Text.tex
cylindric background

\author{Daniel Rogozin}
\date{}
\title{Representable cylindric algebras of dimension $\omega$: the aspects of canonicity}

@@

\begin{enumerate}
  \item There exists $\iota : \mathcal{A} \hookrightarrow \mathcal{A}^{+}$ such that
  $\iota : a \mapsto \{ \gamma \in {\bf Uf}(\mathcal{A}) \: | \: a \in \gamma \}$.
  \item If $i : \mathcal{A} \hookrightarrow \mathcal{B}$, then this embedding might be extented to the embedding
  $i^{+} : \mathcal{A}^{+} \hookrightarrow \mathcal{B}^{+}$
\end{enumerate}
\end{theorem}

@@

\subsection{(Representable) cylindric algebras and cylindric set algebras}

Cylindric algebras provide a generalisation of relation algebras for relations of an arbitrary arity. Let $\alpha$ be an ordinal. Let $\prescript{\alpha}{}U$ be the set of all functions mapping $\alpha$ to a non-empty set $U$. We denote $x(i) = x_i$ for
$x \in \prescript{\alpha}{}U$ and $i < \alpha$.

@@

The following definition is due to \cite{sankappanavar1981course}:

@@

\begin{defin}
  A cylindic set algebra of dimension $\alpha$ is an algebra consisting of a set $S$ of $\alpha$-ry relation on some base set $U$
    with the constants and operations $0 = \emptyset$, $1 = \prescript{\alpha}{}U$, $\cap$, $-$, the diagonal elements $\{ D_{ij} \}_{i, j < \alpha}$, the cylindrifications $\{ C_i \}_{i < \alpha}$. A generalised cylindric set algebra of dimension $\alpha$ is a subdirect of cylindric algebras that have dimension $\alpha$
\end{defin}

\begin{defin}
    A cylindric algebra of dimension $\alpha$ is an algebra $\mathcal{C} = \langle \mathcal{B}, \{ c_i \}_{i < \alpha}, \{ d_{ij} \}_{i, j < \alpha} \rangle$ such that
    \begin{itemize}
      \item $\mathcal{B}$ is a Boolean algebra, for each $i, j < \alpha$ $c_i$ is an operator and $d_{ij} \in \mathcal{B}$
      \item For each $i < \alpha$, $a \leq c_i a$, $c_i (a \land c_i b) = c_i a \land c_i b$ and $d_{ii} = 1$
      \item For every $i, j < \alpha$, $c_i c_j a = c_j c_i a$
      \item If $k \neq i, j < \alpha$, then $d_{ij} = c_k (d_{ij} \land d_{jk})$
      \item If $i \neq j$, then $c_i (d_{ij} \land a) \land c_i (d_{ij} \land - a) = 0$
    \end{itemize}
    ${\bf CA}_{\alpha}$ is the class of all cylindric algebras of dimension $\alpha$
\end{defin}

@@

Let $\mathcal{A} \in {\bf C}_{\omega}$, then $\mathcal{A}$ has a \emph{complete representation}, if this representation preserves all existing suprema. In other words, $\mathcal{A}$ is completely representable.

@@

Let us discuss the connection between representability and canonical extensions.

@@

In particular, an element $x$ is called \emph{zero-dimensional} if $\Delta x = 0$. Zero-dimensional elements reflect equivalence classes of sentences in the Lindenbaum-Tarski algebra of a given first-order theory. Thus, the set of zero-dimensional elements form a Boolean algebras of sentences associated with $\Theta$.

@@

@@

\begin{defin}
  Let $\mathcal{A}$ be a BAO of type ${\bf CA}_{\omega}$, an $\mathcal{A}$-pre-network is a pair
  $\mathcal{N} = \langle N, l \rangle$, where $N$ is a set of nodes and $l : \prescript{\omega}{}N \to \operatorname{At}(\mathcal{A})$.

@@

\begin{defin}
  Let $\mathcal{A}$ be an atomic BAO of type ${\bf CA}_{\omega}$ and $\kappa > 0$ a cardinal. The game $\mathcal{G}^{\kappa}(\mathcal{A})$ is defined as follows. The game has two players: $\forall$ (Abelard, he/his) and $\exists$ (H\'{e}lo\"{i}se, she/her). A play of the game $\mathcal{G}^{\kappa}(\mathcal{A})$ is the sequence of networks
  \begin{center}
    $\mathcal{N}_0 \subseteq \mathcal{N}_1 \subseteq \mathcal{N}_2 \subseteq \dots \subseteq \mathcal{N}_{\lambda} \subseteq \dots$ for $\lambda < \kappa$
  \end{center}
  The game consists of the following stages:
  \begin{enumerate}
    \item ({\bf Zero round})

@@

    Let $0 < \lambda$ be a cardinal such that $\lambda + 1 < \kappa$ and a network $\mathcal{N}_{\lambda} = \langle N_{\lambda}, l_{\lambda} \rangle$ has been already played.

    $\forall$ picks $i < \omega$, $x \in \prescript{\omega}{}N_{\lambda}$, $a \in \operatorname{At}$ such that $l_{\lambda}(x) \leq c_i a$.
    We denote this move as $(i, x, a)$. $\exists$ responds with a network $\mathcal{N}_{\lambda + 1} \supseteq \mathcal{N}_{\lambda}$. $\forall$ wins, if there is no node $c \in N$ such that $l_{\lambda+1}(x[i/c]) = a$, then $\forall$ wins
    \item The limit of the play is defined as $\bigcup \limits_{\lambda < \kappa} \mathcal{N}_{\lambda}$. $\forall$ wins the play, if there exists $\kappa_1 < \kappa$ such that $\exists$ does not win the $\kappa_1$th-round. Otherwise, $\exists$ wins the play.
  \end{enumerate}
\end{defin}

@@

  \begin{enumerate}
    \item $\mathcal{A}$ is completely representable.
    \item $\exists$ has a winning strategy in $\mathcal{G}^{\kappa + \omega}$.
  \end{enumerate}
\end{theorem}

@@

    Suppose $\exists$ has a winning strategy in $\mathcal{G}^{\kappa + \omega}(\mathcal{A})$.
    In every round $\forall$ picks all possible $i < \omega$, $a \in \operatorname{At}(\mathcal{A})$, all possible hyperedges and all appropriate atoms and $\exists$ has a proper response for every $\forall$'s move.

@@

    So we define a map $rep$:
    \begin{center}
    $rep(a) = \{ x \: | \: \exists b \in \operatorname{At}(\mathcal{A}) \: x \in \prescript{\omega}{}N_a, l_a(x) \leq b \}$.
  \end{center}
    We check that $rep$ preserves cylindrifications and diagonal elements. Let $i, j < \omega$ and $a \in \mathcal{A}$:
    \begin{enumerate}
    \item Suppose $x \in rep(c_i a)$, then there exists an atom $b$ such that $x \in \prescript{\omega}{}N_b$ with $l_b(x) \leq c_i a$. Then there exists $y \equiv_i x$ with $l_b(y) \leq a$, so $x \in {\bf C}_i(rep(a))$.

    Let $x \in {\bf C}_i(rep(a))$. We need $x \in (rep(c_i a))$, that is, one needs to find an atom $c$ such that $l_c(x) \leq c_i a$.

    We already know that there exists $y \equiv_i x$ such that $y \in rep(a)$, that is, there exists an atom $b$ such that $y \in \prescript{\omega}{}N_b$ and $l_b(y) \leq a$.

    \item If $x \in rep(d_{ij})$, so there exists an atom $b$ with $x \in \prescript{\omega}{}N_a$ and $l_b(x) \leq d_{ij}$, then $x_i = x_j$, then $x \in D_{ij}$.
    \end{enumerate}
  \end{enumerate}
\end{proof}

@@

  The argument uses \L o\'s's Theorem, see \cite[Theorem 8.5.3]{hodges1997shorter}.

@@

@@

  Consider $\rho(\mathcal{A})$. Let us show that $\exists$ has a winning strategy on $\mathcal{G}^{\kappa + \omega}(\rho(\mathcal{A}))$
\end{proof}

>>>>

\author{Daniel Rogozin}
\date{}
\title{Representable cylindric algebras of dimension $\omega$: the aspects of canonicity and axiomatisability}

@@

\begin{enumerate}
  \item There exists $\iota : \mathcal{A} \hookrightarrow \mathcal{A}^{+}$ such that
  $\iota : a \mapsto \{ \gamma \in {\bf Uf}(\mathcal{A}) \: | \: a \in \gamma \}$.
  \item $i : \mathcal{A} \hookrightarrow \mathcal{B}$ implies
  $i^{+} : \mathcal{A}^{+} \hookrightarrow \mathcal{B}^{+}$
\end{enumerate}
\end{theorem}

@@

\section{Cylindric algebras and cylindric set algebras}

 Let $\alpha$ be an ordinal. Let $\prescript{\alpha}{}U$ be the set of all functions mapping $\alpha$ to a non-empty set $U$. We denote $x(i) = x_i$ for
$x \in \prescript{\alpha}{}U$ and $i < \alpha$.

@@

The following definition is due to, e.g., \cite{sankappanavar1981course}:

@@

\begin{defin}
  A cylindic set algebra of dimension $\alpha$ is an algebra consisting of a set $S$ of $\alpha$-ry relation on some base set $U$
    with the constants and operations $0 = \emptyset$, $1 = \prescript{\alpha}{}U$, $\cap$, $-$, the diagonal elements $\{ D_{ij} \}_{i, j < \alpha}$, the cylindrifications $\{ C_i \}_{i < \alpha}$. A generalised cylindric set algebra of dimension $\alpha$ is a subdirect of cylindric algebras that have dimension $\alpha$.
\end{defin}

\begin{defin}
    A cylindric algebra of dimension $\alpha$ is an algebra $\mathcal{C} = \langle \mathcal{B}, \{ c_i \}_{i < \alpha}, \{ d_{ij} \}_{i, j < \alpha} \rangle$ such that
    \begin{itemize}
      \item $\mathcal{B}$ is a Boolean algebra, for each $i, j < \alpha$ $c_i$ is an operator and $d_{ij} \in \mathcal{B}$
      \item For each $i < \alpha$, $a \leq c_i a$, $c_i (a \land c_i b) = c_i a \land c_i b$ and $d_{ii} = 1$
      \item For every $i, j < \alpha$, $c_i c_j a = c_j c_i a$
      \item If $k \neq i, j < \alpha$, then $d_{ij} = c_k (d_{ij} \land d_{jk})$
      \item If $i \neq j$, then $c_i (d_{ij} \land a) \land c_i (d_{ij} \land - a) = 0$
    \end{itemize}
    ${\bf CA}_{\alpha}$ is the class of all cylindric algebras of dimension $\alpha$.
\end{defin}

\begin{defin}
  Let $\mathcal{A} = \langle A, +, -, 0, 1, (c_i)_{i < \alpha}, (d_ij)_{i,j < \alpha} \rangle \in {\bf CA}_{\alpha}$ and $\beta < \alpha$, then the $\beta$-reduct of $\mathcal{A}$ is an algebra $\mathcal{A}_{\beta} = \langle A, +, -, 0, 1, (c_i)_{i < \beta}, (d_ij)_{i,j < \beta} \rangle$,
\end{defin}

@@

Let $\mathcal{A} \in {\bf CA}_{\omega}$, then $\mathcal{A}$ has a \emph{complete representation}, if this representation preserves all existing suprema. In other words, $\mathcal{A}$ is completely representable.

@@

\subsection{Closed elements}

@@

In particular, an element $x$ is called \emph{zero-dimensional} if $\Delta x = 0$. Zero-dimensional elements correspond to equivalence classes of sentences in the Lindenbaum-Tarski algebra of a given first-order theory. Thus, the set of zero-dimensional elements form a Boolean algebras of sentences associated with $\Theta$.

@@

\subsection{Neat reducts}

@@

\begin{defin} \label{network}
  Let $\mathcal{A}$ be a BAO of type ${\bf CA}_{\omega}$, an $\mathcal{A}$-pre-network is a pair
  $\mathcal{N} = \langle N, l \rangle$, where $N$ is a set of nodes and $l : \prescript{\omega}{}N \to \operatorname{At}(\mathcal{A})$.

@@

\begin{defin} Let $n \leq \omega$ an $\mathcal{A}$ be an atomic BAO of type ${\bf CA}_{\omega}$ that has countably atoms. The game $\mathcal{G}_{n}(\mathcal{A})$ is defined as follows. The game has two players: $\forall$ (Abelard, he/his) and $\exists$ (H\'{e}lo\"{i}se, she/her). A play of the game $\mathcal{G}_{n}(\mathcal{A})$ is the sequence of networks
  \begin{center}
    $\mathcal{N}_0 \subseteq \mathcal{N}_1 \subseteq \mathcal{N}_2 \subseteq \dots \subseteq \mathcal{N}_{k} \subseteq \dots$ for $k < n$
  \end{center}
  The game consists of the following stages:
  \begin{enumerate}
    \item ({\bf Zero round})

@@

    Let $k < n$ such that $k + 1 < \kappa$ and a network $\mathcal{N}_{\lambda} = \langle N_{k}, l_{k} \rangle$ has been already played.

    $\forall$ picks $i \leq k$, $x \in \prescript{\omega}{}N_{k}$, $a \in \operatorname{At}(\mathcal{A})$ such that $l_{k}(x) \leq c_i a$.
    We denote this move as $(i, x, a)$. $\exists$ responds with a network $\mathcal{N}_{k + 1} \supseteq \mathcal{N}_{k}$. $\forall$ wins, if there is no node $c \in N$ such that $l_{\lambda+1}(x[i/c]) = a$, then $\forall$ wins
    \item The limit of the play is defined as $\bigcup \limits_{k < n} \mathcal{N}_{k}$. $\forall$ wins the play, if there exists $m < n$ such that $\exists$ does not win the $m$-th round. Otherwise, $\exists$ wins the play.
  \end{enumerate}
\end{defin}

@@

  \begin{enumerate}
    \item $\mathcal{A}$ is completely representable.
    \item $\exists$ has a winning strategy in $\mathcal{G}_{\kappa + \omega}$.
  \end{enumerate}
\end{theorem}

@@

    Suppose $\exists$ has a winning strategy in $\mathcal{G}_{\kappa + \omega}(\mathcal{A})$.
    In every round $\forall$ picks all possible $i < \omega$, $a \in \operatorname{At}(\mathcal{A})$, all possible hyperedges and all appropriate atoms and $\exists$ has a proper response for every $\forall$'s move.

@@

    So we define a map $rep$:
    \begin{center}
    $\operatorname{rep}(a) = \{ x \: | \: \exists b \in \operatorname{At}(\mathcal{A}) \: x \in \prescript{\omega}{}N_a, l_a(x) \leq b \}$.
  \end{center}
    We check that $rep$ preserves cylindrifications and diagonal elements. Let $i, j < \omega$ and $a \in \mathcal{A}$:
    \begin{enumerate}
    \item Suppose $x \in \operatorname{rep}(c_i a)$, then there exists an atom $b$ such that $x \in \prescript{\omega}{}N_b$ with $l_b(x) \leq c_i a$. Then there exists $y \equiv_i x$ with $l_b(y) \leq a$, so $x \in {\bf C}_i(\operatorname{rep}(a))$.

    Let $x \in {\bf C}_i(\operatorname{rep}(a))$. We need $x \in (\operatorname{rep}(c_i a))$, that is, one needs to find an atom $c$ such that $l_c(x) \leq c_i a$.

    We already know that there exists $y \equiv_i x$ such that $y \in \operatorname{rep}(a)$, that is, there exists an atom $b$ such that $y \in \prescript{\omega}{}N_b$ and $l_b(y) \leq a$.

    \item If $x \in \operatorname{rep}(d_{ij})$, so there exists an atom $b$ with $x \in \prescript{\omega}{}N_a$ and $l_b(x) \leq d_{ij}$, then $x_i = x_j$, then $x \in D_{ij}$.
    \end{enumerate}
  \end{enumerate}
\end{proof}

If $\mathcal{A} \in {\bf CA}_{n}$ is atomic, then we have the following criterion of complete representability formulated in terms of back-and-forth games, see \cite[Theorem 3.3.3 and Corollary 3.3.5]{hirsch2013completions}. Here, the definition of a network for the case of ${\bf CA}_n$ is the same as Definition~\ref{network}, but hyperedges have lenght $n$.

\begin{theorem}
  Let $\mathcal{A}$ be an atomic BAO of type ${\bf CA}_n$ such that $|\operatorname{At}(\mathcal{A})| = \kappa$, where $\kappa$ is an arbitrary cardinal. Then the following are equivalent:

  \begin{enumerate}
    \item $\mathcal{A}$ is completely representable iff $\exists$ has a winning strategy in $\mathcal{G}_{\kappa + \omega}(\mathcal{A})$.
    \item $\exists$ has a winning strategy in $\mathcal{G}_{m}(\mathcal{A})$ for every $m < \omega$ iff $\mathcal{A}$ is elementarily equivalent to a completely representable cylindric algebra.
  \end{enumerate}
\end{theorem}

Now we formulate the Lyndon conditions for BAOs of type ${\bf CA}_{\omega}$, but we need their analogues for the finite case which are due to \cite[Theorem 34]{hirsch1997step}. Let $\mathcal{A}$ be an atomic BAO of type ${\bf CA}_{n}$. $lc_k^n$ is a first-order sentence such that $\mathcal{A} \models lc_k^n$ iff $\exists$ has a winning strategy in the game $\mathcal{G}_k(\mathcal{A})$ of length $k < \omega$.

Consider the following set of formulas:
\begin{center}
  $LC_{\omega} = \{ lc_n^n \: | \: n < \omega \}$
\end{center}
We shall think of $LC_{\omega}$ as the Lyndon conditions for atomic cylindric algebras of dimension $\omega$. Let us write down those $lc_n^n$s explicitly, this is due to \cite[Sections 11.3 and 11.4]{hirsch1997step}. For that, we need a bit of definitions.

\begin{proposition}
  Let $\mathcal{A}$ be a BAO of type ${\bf CA}_{\omega}$ and $m < \omega$, then $\exists$ has a winning strategy in $\mathcal{G}_m(\mathcal{A})$ iff $\mathcal{A}_m \models lc(m,m)$
\end{proposition}

\begin{proof}
\end{proof}

Let us recall the definition of an ultraproduct, see \cite[Section 9.5]{hodges1993model}. Let $I$ be an index set, $U$ an ultrafiler over $I$, an $(\mathcal{A}_i)_{i \in I}$ a family of structures of the same signature. The ultraproduct of $(\mathcal{A}_i)_{i \in I}$ modulo $U$, denoted as $\Pi_U \mathcal{A}_i$, is an algebra of the same signature whose elements are elements of the direct product
$\Pi_{i \in I} \mathcal{A}_i$ factorised through an equivalence relation $\sim$ such that for every $a, b \in \Pi_{i \in I} \mathcal{A}_i$:
\begin{center}
  $a \sim b \Leftrightarrow \{ i \in I \: | \: a(i) = b(i)\} \in U$
\end{center}

\begin{lemma}
  Let $\mathcal{A}$ be an atomic BAO of type ${\bf CA}_{\omega}$ such that for every $n < \omega$ $\mathcal{A}_n \models lc(n,n)$, then $\exists$ has a winning strategy in $\mathcal{G}_{\omega}(\Pi_U \mathcal{A})$, where $\Pi_U \mathcal{A}$ is a non-principal ultrapower of $\mathcal{A}$ and $U$ is a non-principal ultrafilter over $\omega$.
\end{lemma}

\begin{proof}
  Suppose $\mathcal{A}_n \models lc(n,n)$ for each $n$.
\end{proof}

\begin{theorem}
  What's going on? :(
\end{theorem}

@@

  The argument uses \L o\'s's Theorem, see \cite[Theorem 9.5.1]{hodges1993model}.

@@

\begin{theorem}
  The elementary closure of the class of completely representable cylindric algebras of dimension $\omega$ is axiomatised with the axioms of ${\bf CA}_{\omega}$ and the Lyndon conditions.
\end{theorem}

@@

  Consider $\rho(\mathcal{A})$. Let us show that $\exists$ has a winning strategy on $\mathcal{G}_{\kappa + \omega}(\rho(\mathcal{A}))$
\end{proof}
